Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-30 fmics/paper.tex
reword last paragraph of introduction

The rest of the paper is organized as follows.
An overview of BLMS and its main components is given in Section~\ref{sec-BLM} and is followed by a description of SRS implementation in Section~\ref{sec-SRS}.
The verification approach of SRS is presented in Section~\ref{sec-verification}.
We conclude in Section~\ref{sec-conclusions} with a summary of lessons learned and future directions.

>>>>

Our contributions in this paper are: a formal model of the SRS component of the BLMS, and commentary on the process and outcomes of taking a formal approach.
We give an overview of the BLMS in Section~\ref{sec-BLM}, and describe the SRS component in particular in Section~\ref{sec-SRS}.
In Section~\ref{sec-verification} we describe our approach to formal verification, and present the formal model and results.
Finally, we reflect on the process, summarising lessons learned and future directions, in Section~\ref{sec-conclusions}.
